Capstone Movielens Report

### 2025-12-09 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix.

::: {.noteblock data-latex=""}
In the sample code snippet above, the `mean_reg` function is called internally from the [train_user_movie_effect](#func.train_user_movie_effect) function described below in section *Models Training: Support Functions \* [UME Model: Utility Functions] of *this Appendix*.
:::
:::

@@

:::
::: { #func.mean_reg.args.lambda .sidebar }
  - **lambda:** (0 by default) _Regularization parameter_ $\lambda$ used in the _Regularization techniques_.

>>>>

::: {.noteblock data-latex=""}
In the sample code snippet above, the `mean_reg` function is called internally from the [train_user_movie_effect](#func.train_user_movie_effect) function described below in section *Models Training: Support Functions /* [UME Model: Utility Functions] of *this Appendix*.
:::
:::

@@

:::
::: { #func.mean_reg.args.lambda .sidebar }
  - **lambda:** (0 by default) _Regularization parameter_ $\lambda$.
